Random Generation of Rich \\ Abstract Data Type Values

### 2019-01-26 paper/tikz/hrep.tex
Done for today
Added evaluation

%Right Arrow [id:dp7732858674364509]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (340,255) -- (340,195) -- (335,195) -- (345,195) -- (355,195) -- (350,195) -- (350,255) -- cycle ;
%Right Arrow [id:dp2590973168233759]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (311,190) -- (360.31,190) -- (360.31,185) -- (376,195) -- (360.31,205) -- (360.31,200) -- (311,200) -- cycle ;
%Shape: Rectangle [id:dp2141233912633571]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (231,125) -- (321,125) -- (321,255) -- (231,255) -- cycle ;
%Right Arrow [id:dp06215174722463401]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,161.75) -- (228.69,161.75) -- (228.69,158) -- (241,165.5) -- (228.69,173) -- (228.69,169.25) -- (171,169.25) -- cycle ;
%Right Arrow [id:dp6766910698477273]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,196.75) -- (228.69,196.75) -- (228.69,193) -- (241,200.5) -- (228.69,208) -- (228.69,204.25) -- (171,204.25) -- cycle ;
%Right Arrow [id:dp3196923724356615]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,230.75) -- (228.69,230.75) -- (228.69,227) -- (241,234.5) -- (228.69,242) -- (228.69,238.25) -- (171,238.25) -- cycle ;
%Right Arrow [id:dp0360549353694295]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (431,190) -- (480.31,190) -- (480.31,185) -- (496,195) -- (480.31,205) -- (480.31,200) -- (431,200) -- cycle ;
%Shape: Rectangle [id:dp2934677500856828]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (496,125) -- (596,125) -- (596,255) -- (496,255) -- cycle ;
%Straight Lines [id:da7152551743774183]
\draw    (558.5,207.5) -- (568.5,217) ;

@@

% Text Node
\draw (85,133.5) node [scale=0.8]  {$\text{\textbf{module}}\ M$};
% Text Node
\draw (100,159.5) node [scale=0.8]  {$\text{\textbf{data}}\ Html\ =\ ... $};
% Text Node
\draw (107,219.5) node [scale=0.8]  {$div::Html\rightarrow Html$};
% Text Node
\draw (109,233.5) node [scale=0.8]  {$bold::Html\rightarrow Html$};
% Text Node
\draw (86,246.5) node [scale=0.8]  {$hr::Html$};
% Text Node
\draw (275.5,135.5) node [scale=0.8]  {$Html_{Spec}$};
% Text Node
\draw (276,165) node [scale=0.8]  {$Html_{ADT}$};
% Text Node
\draw (276,200) node [scale=0.8]  {$Html_{Patterns}$};
% Text Node
\draw (276,235) node [scale=0.8]  {$Html_{Interface}$};
% Text Node
\draw (276,182.5) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (276,217.5) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (405.5,133.5) node [scale=0.8]  {$Generator$};
% Text Node
\draw (406,178) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (406,217.5) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (514.5,133.5) node [scale=0.8]  {$Html$};
% Text Node
\draw (100,184.5) node [scale=0.8]  {$simpl\ ( ...) \ =\ ... \ $};
% Text Node
\draw (100,198.5) node [scale=0.8]  {$simpl\ ( ...) \ =\ ... \ $};
% Text Node
\draw (202.5,142.5) node [scale=0.7] [align=left] {\textbf{Structure}\\ \textbf{reification}};
% Text Node
\draw (348.5,169.5) node [scale=0.7] [align=left] {\textbf{Generator}\\ \textbf{derivation}};
% Text Node
\draw (466,168.5) node [scale=0.7] [align=left] {\textbf{Random} \\ \textbf{generation}};
% Text Node
\draw (346.5,272.5) node [scale=0.7] [align=left] {\textbf{User desired} \\ \textbf{distribution}};

>>>>

%Right Arrow [id:dp7732858674364509]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (340,230) -- (340,195) -- (335,195) -- (345,195) -- (355,195) -- (350,195) -- (350,230) -- cycle ;
%Right Arrow [id:dp2590973168233759]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (311,190) -- (360.31,190) -- (360.31,185) -- (376,195) -- (360.31,205) -- (360.31,200) -- (311,200) -- cycle ;
%Shape: Rectangle [id:dp2141233912633571]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (231,125) -- (321,125) -- (321,255) -- (231,255) -- cycle ;
%Right Arrow [id:dp06215174722463401]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,161.75) -- (228.69,161.75) -- (228.69,158) -- (241,165.5) -- (228.69,173) -- (228.69,169.25) -- (171,169.25) -- cycle ;
%Right Arrow [id:dp6766910698477273]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,196.75) -- (228.69,196.75) -- (228.69,193) -- (241,200.5) -- (228.69,208) -- (228.69,204.25) -- (171,204.25) -- cycle ;
%Right Arrow [id:dp3196923724356615]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (171,230.75) -- (228.69,230.75) -- (228.69,227) -- (241,234.5) -- (228.69,242) -- (228.69,238.25) -- (171,238.25) -- cycle ;
%Right Arrow [id:dp0360549353694295]
\draw  [fill={rgb, 255:red, 226; green, 226; blue, 226 }  ,fill opacity=1 ] (431,190) -- (480.31,190) -- (480.31,185) -- (496,195) -- (480.31,205) -- (480.31,200) -- (431,200) -- cycle ;
%Shape: Rectangle [id:dp2934677500856828]
\draw  [fill={rgb, 255:red, 255; green, 255; blue, 255 }  ,fill opacity=1 ] (496,125) -- (596,125) -- (596,255) -- (496,255) -- cycle ;
%Straight Lines [id:da7152551743774183]
\draw    (558.5,207.5) -- (568.5,217) ;

@@

% Text Node
\draw (85,133.5) node [scale=0.8]  {$\text{\textbf{module}}\ M$};
% Text Node
\draw (100,159.5) node [scale=0.8]  {$\text{\textbf{data}}\ Html\ =\ ... $};
% Text Node
\draw (107,219.5) node [scale=0.8]  {$div::Html\rightarrow Html$};
% Text Node
\draw (109,233.5) node [scale=0.8]  {$bold::Html\rightarrow Html$};
% Text Node
\draw (86,246.5) node [scale=0.8]  {$hr::Html$};
% Text Node
\draw (275.5,135.5) node [scale=0.8]  {$Html_{Spec}$};
% Text Node
\draw (276,165) node [scale=0.8]  {$Html_{ADT}$};
% Text Node
\draw (276,200) node [scale=0.8]  {$Html_{Patterns}$};
% Text Node
\draw (276,235) node [scale=0.8]  {$Html_{Interface}$};
% Text Node
\draw (276,182.5) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (276,217.5) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (405.5,133.5) node [scale=0.8]  {$Generator$};
% Text Node
\draw (406,178) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (406,217.5) node   {$\boldsymbol{\oplus}$};
% Text Node
\draw (514.5,133.5) node [scale=0.8]  {$Html$};
% Text Node
\draw (100,184.5) node [scale=0.8]  {$simpl\ ( ...) \ =\ ... \ $};
% Text Node
\draw (100,198.5) node [scale=0.8]  {$simpl\ ( ...) \ =\ ... \ $};
% Text Node
\draw (202.5,142.5) node [scale=0.7] [align=left] {\textbf{Structure}\\ \textbf{specification}};
% Text Node
\draw (348.5,169.5) node [scale=0.7] [align=left] {\textbf{Generator}\\ \textbf{derivation}};
% Text Node
\draw (466,168.5) node [scale=0.7] [align=left] {\textbf{Random} \\ \textbf{generation}};
% Text Node
\draw (348,245) node [scale=0.7] [align=left] {\textbf{User desired} \\ \textbf{distribution}};
